---
title: "test"
output: learnr::tutorial
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
library(learnr)
library(checkr)
library(tidyverse)
library(datasets)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)

library(ggplot2movies)
data(movies)

```


```{r exe22-setup, echo = FALSE}

```

#```{r exe22, exercise = TRUE, exercise.setup = "exe22-setup", exercise.eval = FALSE}
```{r exe3, exercise = TRUE}
movies1 <- movies %>% select(title,votes,mpaa,rating, Action:Short) %>%
  filter(votes > 200, mpaa!="")

```

```{r exe3-solution, echo = FALSE}
movies1 <- movies %>% select(title,votes,mpaa,rating, Action:Short) %>%
  filter(votes > 200, mpaa!="")

```

```{r exe3-check, echo = FALSE}
# USER_CODE <- capture.code('movies1 <- movies %>% select(title,votes,mpaa,rating, Action:Short) %>%
#   filter(votes > 200, mpaa!="")')

test_1 <- find_call("select()", "you didn's use select()")
test_2 <- find_names("movies", "you didn't use `movies` dataset") 
test_3 <- find_names("title", "select `title` variable")
test_4 <- find_names("votes", "select `votes` variable")
test_5 <- find_names("mpaa", "select `mpaa` variable")
test_6 <- find_names("rating", "select `ratings` variable")
test_7 <- find_names("Action", "select `Action` variable")
test_8 <- find_names("Short", "select `Short` variable")
test_9 <- find_call("filter()", "you didn't use filter()")

# c & получается типа, но оно ненадежно. с запятой уже не раб. порядок тоджк вроде
test_10 <- find_call('votes > 200 & mpaa != ""', "mpaa")

# test_10 <- check_argument("... = grab_this", check_value(x == "votes > 200"), "you didn't filter movies with less or equal to 200 votes")
# test_11 <- check_argument("mpaa!= grab_this", agrees(x == ""), "fuc u")
# test_11 <- find_statement('!=', "")
# test_12 <- find_statement('mpaa!=""', "mpaa")

USER_CODE %>% test_1 %>% test_2  %>%  test_3 %>% test_4 %>% test_5 %>% test_6 %>% test_7  %>%  test_8 %>% test_9 %>% test_10 #%>% test_11 #%>% test_10
 
```


flData = nycflights13::flights
flData = na.omit(flData)

flData = filter(flData, month == 6 | month == 7 | month == 8)
flData = filter(flData, dest == "MIA")
flData = arrange(flData, year, month, day)
flData = arrange(flData, desc(dep_delay))
flData = dplyr::select(flData, tail_num = tailnum, dep_delay:arr_delay)
flData = dplyr::select(flData, -arr_time)
flData = mutate(flData, dep_arr_dif = arr_delay - dep_delay)
flData = group_by(flData, tail_num)
tail_dif = dplyr::summarise(flData, median_dif = median(dep_arr_dif))
flData = inner_join(x = flData, y = tail_dif, by = "tail_num")

flData = arrange(flData, median_dif)
